---
title: "ITBI Data"
---

```{r}
library(tidyverse)
```

# Collecting Census tracts

In addition to the ITBI data, we will also need to collect data on the census tracts in São Paulo. The census tracts will allow us to aggregate the ITBI data at the census tract level and analyze the impact of flooding events on real estate prices and liquidity with a higher level of granularity that takes demographic and geographic factors into account.

```{r}
options(scipen = 32)
data_dir <- "data"
dir.create(data_dir, showWarnings = FALSE)
census_data_dir <- file.path(data_dir, "census")
dir.create(census_data_dir, showWarnings = FALSE)
```

```{r}
# read the census tracts data from geobr
census_tracts <- geobr::read_census_tract(code_tract = 3550308, year = 2022)
census_tracts |> head(200) |> DT::datatable()
```

# Collecting Census Data

Based on the documentation of `censobr` package, we need the following variables:

- raca_V01318: color/race is black
- raca_V01320: color/race is brown
- raca_V01321: color/race is indigenous
- V0001: total population

```{r}
# read the census data from censobr
tracts_basic <- censobr::read_tracts(year = 2022, dataset = "Basico")
tracts_people <- censobr::read_tracts(year = 2022, dataset = "Pessoas")
```

```{r}
tracts_basic <- tracts_basic |> select(code_tract, V0001)
tracts_people <- tracts_people |> select(code_tract, raca_V01318, raca_V01320, raca_V01321)

census_tracts <- census_tracts |>
    left_join(tracts_basic, by = "code_tract", copy=TRUE) |>
    left_join(tracts_people, by = "code_tract", copy=TRUE) |>
    mutate(
        pct_black = raca_V01318 / V0001,
        pct_brown = raca_V01320 / V0001,
        pct_indigenous = raca_V01321 / V0001
    ) |>
    select(-raca_V01318, -raca_V01320, -raca_V01321)
```

```{r}
sfarrow::st_write_parquet(census_tracts, file.path(census_data_dir, "census_tracts.parquet"))
```