---
title: "Flood data Data"
---

Now, with the transactions and flood events data collected, we can start preparing the data for the actual regression model. The first approach we will take is to aggregate the data by week, creating a database of house records with a dummy variable indicating whether it has been transacted in that week or not, and a expose variable with the sum of the inverse distance to all of the flood events that happened in the same week. We will also need to select a cap distance for the flood events, as we will not consider events that are too far away from the house.

```{r}
library(tidyverse)
library(janitor)
library(geoarrow)
library(arrow)
library(sf)
library(units)
library(tmap)
```

First, let's load the ITBI data and the flood events data that we have previously collected.

```{r}
itbi_data <- read_parquet("data/itbi/itbi_2025_geocoded.parquet")
itbi_data$geometry <- st_as_sfc(itbi_data$geometry)
st_geometry(itbi_data) <- "geometry"
flood_events <- st_read("data/occurrence/flood_events.gpkg")
```

Let's confirm that both datasets are using the same coordinate reference system (CRS). If they are not, we will need to transform one of them to match the other.

```{r}
st_crs(itbi_data)
st_crs(flood_events)
```

The itbi_data is in EPSG:4674, while the flood_events is in EPSG:31983. We will transform the itbi_data to match the flood_events CRS.

```{r}
itbi_data <- st_transform(itbi_data, crs = st_crs(flood_events))
```

# Specifying the characteristics of the houses on the observations

## Keeping residential houses only

The first step in preparing the data for the regression model is to filter the itbi_data to keep only the residential houses. We will use the `descricao_do_padrao_iptu` column to filter the data.

```{r}
itbi_data |>
    st_drop_geometry() |>
    select(descricao_do_padrao_iptu) |>
    distinct() |>
    arrange(descricao_do_padrao_iptu) |>
    DT::datatable()
```

```{r}
residential_houses <- itbi_data |>
    filter(str_detect(descricao_do_padrao_iptu, "RESIDENCIAL"))

residential_houses |> glimpse()
```

## Selecting the geocoding precision

The next step is to filter the itbi_data to keep only the houses that have been geocoded with a high precision. We will use the `precisao` and `desvio_metros` columns to filter the data. First, let's check the frequency of the different values in the `precisao` column.

```{r}
residential_houses |>
    st_drop_geometry() |>
    select(precisao) |>
    group_by(precisao) |>
    summarise(count = n()) |>
    mutate(percentage = count / sum(count) * 100, percentage = round(percentage, 2)) |>
    arrange(desc(count)) |>
    DT::datatable()
```

Most of the houses have been geocoded with a high precision, so let's drop the houses that have been geocoded by any level above of "numero_aproximado".

```{r}
residential_houses <- residential_houses |>
    filter(precisao %in% c("numero", "numero_aproximado"))
residential_houses |> glimpse()
```

Now, let's check the distribution of the `desvio_metros` column to see if we can filter the data further.

```{r}
residential_houses |>
    st_drop_geometry() |>
    select(desvio_metros) |>
    filter(!is.na(desvio_metros)) |>
    ggplot(aes(x = desvio_metros)) +
    geom_histogram(binwidth = 10, fill = "lightblue", color = "black") +
    labs(title = "Distribution of Geocoding Deviation (meters)", x = "Deviation (meters)", y = "Density") +
    theme_minimal()
```

Again, most of the houses have a low deviation, so let's drop the houses that have a deviation above 50 meters.

```{r}
residential_houses <- residential_houses |>
    filter(desvio_metros <= 50)

residential_houses |> glimpse()
```

## Selecting the cap distance for flood events

Lastly, before creating the house-week database, it will be useful to filter the database only to potential exposed houses, i.e., houses that are within a certain distance from any flood event. So, even if a house does not have a flood event in the same week, it is more likely to be affected by flooding events than a house that is far away from any flood event and, thus, more valid as a control house. We will use a cap distance of 200 meters for the flood events, which is a reasonable distance to consider that a house can be affected by a flooding event.

First, let's create a buffer around the flood events with a radius of 200 meters and dissolve the buffers into a single multipolygon.

```{r}
flood_buffer <- st_buffer(flood_events, dist = 200) |> st_union()

plot(flood_buffer, col = "lightblue", main = "Flood Events Buffer (200m)")
```

Then, we will calculate the distance of each house in the itbi_data to the nearest flood event.[^1]

[^1]: Although we could use the geometry of the buffer to filter the houses or the `st_is_within_distance()` function, we will calculate the distance of each house to the nearest flood event to have more flexibility in the future and ease the sensivity analysis of the cap distance.

```{r}
residential_houses <- residential_houses |>
    # First, enconter the nearest flood event for each house
    mutate(nearest_flood_event_index = st_nearest_feature(geometry, flood_events)) |>
    # Then, calculate the distance to the nearest flood event
    mutate(distance_to_nearest_flood_event = st_distance(geometry, flood_events[nearest_flood_event_index, ], by_element = TRUE))
    # Lastly, delete the nearest_flood_event column, as we don't need it anymore
    # select(-nearest_flood_event_index)
```

Now, let's see the distribution of the distances to the nearest flood event to check if we can filter the data further.

```{r}
residential_houses |>
    st_drop_geometry() |>
    select(distance_to_nearest_flood_event) |>
    filter(!is.na(distance_to_nearest_flood_event)) |>
    ggplot(aes(x = as.numeric(distance_to_nearest_flood_event))) +
    geom_histogram(binwidth = 10, fill = "lightblue", color = "black") +
    labs(title = "Distribution of Distance to Nearest Flood Event (meters)", x = "Distance (meters)", y = "Count of transactions") +
    # Change the x grid to appear in multiples of 50 meters
    scale_x_continuous(breaks = seq(0, 4500, by = 200)) +
    theme_minimal()
```

And the same distribution in a map, with 5 cateories from 0 to 1000 meters, and one category for all distances above 1000 meters.

```{r}
residential_houses |>
    mutate(distance_category = case_when(
        distance_to_nearest_flood_event <= set_units(200, "m") ~ "0-200",
        distance_to_nearest_flood_event <= set_units(400, "m") ~ "201-400",
        distance_to_nearest_flood_event <= set_units(600, "m") ~ "401-600",
        distance_to_nearest_flood_event <= set_units(800, "m") ~ "601-800",
        distance_to_nearest_flood_event <= set_units(1000, "m") ~ "801-1000",
        TRUE ~ ">1000"
    ), distance_category = factor(
        distance_category,
        levels = c("0-200", "201-400", "401-600", "601-800", "801-1000", ">1000")
    )) |>
    tm_shape() +
    # tm_dots(
    #     col = "distance_category",
    #     fill.scale =  tm_scale_categorical(values = "distance_category"),
    #     size = 0.1,
    #     title.col = "Distance (m)"
    # ) +
    tm_symbols(
        size=0.2,
        fill="distance_category",
        fill.scale = tm_scale_categorical(values = "-matplotlib.rd_yl_bu"),
        fill.legend = tm_legend(
            title = "Distance to Nearest Flood Event (m)",
            size=1,
            position = c("right", "top")
        ),
        lwd = 0
    ) +
    tm_legend(
        legend.outside = TRUE,
        legend.position = c("right", "top"),
        title = "Distance to Nearest Flood Event (m)"
    ) +
    tm_title("Distance to Nearest Flood Event")
```

```{r}
# exposed_houses <- itbi_data[st_intersects(residential_houses, flood_buffer, sparse = FALSE), ]
# exposed_houses |> glimpse()
```

# Creating the house-week database

Now, we generate a database with the crossproduct of all houses and all weeks in 2025, and we will create a dummy variable indicating whether the house was transacted in that week or not.

```{r}
houses_2025_unique <- exposed_houses |>
    distinct(n_do_cadastro_sql, .keep_all = TRUE)
```

```{r}
transactions <- exposed_houses |>
    mutate(data_de_transacao = janitor::excel_numeric_to_date(as.numeric(data_de_transacao)),
           week_of_transaction = lubridate::week(data_de_transacao)) |>
    st_drop_geometry() |>
    filter(!is.na(week_of_transaction)) |>
    distinct(n_do_cadastro_sql, week_of_transaction) |>
    mutate(transacted = 1L)
```

```{r}
house_week_db <- houses_2025_unique |>
    st_drop_geometry() |>
    select(n_do_cadastro_sql) |>
    tidyr::crossing(week_of_transaction = 1:53) |>
    left_join(transactions, by = c("n_do_cadastro_sql", "week_of_transaction")) |>
    mutate(transacted = replace_na(transacted, 0L)) |>
    left_join(houses_2025_unique, by = "n_do_cadastro_sql") |>
    st_as_sf()

house_week_db |> glimpse()
```
