---
title: "Flood data Data"

format:
  html:
    embed-resources: true
---

```{r}
library(tidyverse)
library(janitor)
library(geoarrow)
library(arrow)
library(sf)
library(units)
library(tmap)
library(did)
```

# Loading the database

```{r}
data <- sfarrow::st_read_parquet("data/final_database/census_transactions_flooding.parquet")
```

# Running the CS2021 did with multiple quarters

## Selecting the control group

As the staggered treatment adoption assumption, along with homogeneous treatment effects, implies that "the unids do not 'forget' about their treatment experience", we will keep as control group only the units that have not been treated in any period. Specifically, we will keep as control group only the tracts that have no prior flood events since the beginning of the sample period (2013). First, let's see the number of untreated tracts after this filtering before we dive in any further details.

```{r}
no_prior_floods_control <- data |>
    mutate(D = ave(has_flood_event, census_tract, FUN = max)) |>
    filter(
        D == 1 | distance_to_nearest_flood_event > units::set_units(200, "m")
    )
```

```{r}
no_prior_floods_control |>
    sf::st_drop_geometry() |>
    group_by(has_flood_event) |>
    summarise(n = n_distinct(census_tract)) |>
    DT::datatable()
```

There are more than 20,000 tracts in the control group still, which will allow for further stratification of the control group in the future. For now, we will keep the control group as is and run the CS2021 did with multiple periods.

## Creating the `G`, `D` and `t` variables

For the CS2021 DID with multiple periods, I need to create the `G` variable, which indicates the first period in which the unit was treated. Also, lets create a `D` and `t`variable, to keep the data aligned with the notation in CS2021. The `D` variable indicates whether the unit is treated in a given quarter. The `t` variable indicates the quarter in which the unit is observed. The `G` variable will be set to 0 for the control group, and to the first quarter in which the unit was treated for the treated group.

```{r}
no_prior_floods_control <- no_prior_floods_control |>
    mutate(
        D = has_flood_event,
        t = (year - 2023) * 4 + ceiling(month / 3)
    )
    
    
no_prior_floods_control <- no_prior_floods_control |>
    merge(
        no_prior_floods_control |>
            sf::st_drop_geometry() |>
            group_by(census_tract) |>
            summarise(G = max(t*D))
    )

no_prior_floods_control |>
    sf::st_drop_geometry() |>
    group_by(G) |>
    summarise(n = n_distinct(census_tract)) |>
    DT::datatable()
```

## Aggregating by quarter

The `did` package expects the data to have a single observation per unit per period. Therefore, I need to aggregate the data by quarter, summing the number of transactions in each quarter for each unit.

```{r}
no_prior_floods_control <- no_prior_floods_control |>
    group_by(census_tract, t, G, geom) |>
    summarise(
        transactions = sum(transactions)
    ) |>
    ungroup()
```

## Dropping the first quarters for the pre-treatment trends

Lastly, I will drop the first three quarters of the sample, so that there are some quarters before the first treatment period to allow the inspection of the pre-treatment trends. (It is worth noticing that, as we kept only the units that have not been treated in any period as control group, dropping the first quarters will make the treated group to be composed only by units that have been treated after the first three quarters, which is a desirable feature of the sample)

```{r}
no_prior_floods_control <- no_prior_floods_control |>
    filter(G > 3 | G == 0)
```

## Checking for unbalanced groups

```{r}
missing_tracts <- no_prior_floods_control |>
    sf::st_drop_geometry() |>
    group_by(census_tract) |>
    summarise(T = n_distinct(t)) |>
    filter(T < 12) |>
    arrange(desc(T))

missing_tracts |>
    DT::datatable()
```

## Running the CS2021 DID with multiple periods

```{r}
attgt <- did::att_gt(
    yname = "transactions",
    tname = "t",
    idname = "census_tract",
    gname = "G",
    xformla = ~ 1,
    data = no_prior_floods_control
)

summary(attgt)
```

```{r}
ggdid(attgt)
```

```{r}
agg.simple <- aggte(attgt, type = "simple")
summary(agg.simple)
```

```{r}
agg.gs <- aggte(attgt, type = "group")
summary(agg.gs)
```

```{r}
ggdid(agg.gs)
```

```{r}
agg.es <- did::aggte(attgt, type = "dynamic")

summary(agg.es)
```

```{r}
ggdid(agg.es)
```

