---
title: "Flood data Data"

bibliography: 
  - references.bib

format:
  html:
    embed-resources: true
---

```{r}
library(tidyverse)
library(janitor)
library(geoarrow)
library(arrow)
library(sf)
library(units)
library(tmap)
library(did)
library(fixest)
library(did2s)
```

# Loading the database

```{r}
data <- sfarrow::st_read_parquet("data/final_database/census_transactions_flooding.parquet")
```

# Running the CS2021 did with multiple quarters

## Selecting the control group

As the staggered treatment adoption assumption, along with homogeneous treatment effects, implies that "the unids do not 'forget' about their treatment experience", we will keep as control group only the units that have not been treated in any period. Specifically, we will keep as control group only the tracts that have no prior flood events since the beginning of the sample period (2013). First, let's see the number of untreated tracts after this filtering before we dive in any further details.

```{r}
no_prior_floods_control <- data |>
    mutate(D = ave(has_flood_event, census_tract, FUN = max)) |>
    filter(
        D == 1 | distance_to_nearest_flood_event > units::set_units(0, "m")
    )
```

```{r}
no_prior_floods_control |>
    sf::st_drop_geometry() |>
    group_by(has_flood_event) |>
    summarise(n = n_distinct(census_tract)) |>
    DT::datatable()
```

There are more than 20,000 tracts in the control group still, which will allow for further stratification of the control group in the future. For now, we will keep the control group as is and run the CS2021 did with multiple periods.

## Creating the `G`, `D` and `t` variables

For the CS2021 DID with multiple periods, I need to create the `G` variable, which indicates the first period in which the unit was treated. Also, lets create a `D` and `t`variable, to keep the data aligned with the notation in CS2021. The `D` variable indicates whether the unit is treated in a given quarter. The `t` variable indicates the quarter in which the unit is observed. The `G` variable will be set to 0 for the control group, and to the first quarter in which the unit was treated for the treated group.

```{r}
no_prior_floods_control <- no_prior_floods_control |>
    mutate(
        D = has_flood_event,
        t = (year - 2023) * 4 + ceiling(month / 3)
    )
    
    
no_prior_floods_control <- no_prior_floods_control |>
    left_join(
        no_prior_floods_control |>
            sf::st_drop_geometry() |>
            group_by(census_tract) |>
            summarise(G = max(t*D)),
        by = "census_tract"
    )

no_prior_floods_control |>
    sf::st_drop_geometry() |>
    group_by(G) |>
    summarise(n = n_distinct(census_tract)) |>
    DT::datatable()
```

## Aggregating by quarter

The `did` package expects the data to have a single observation per unit per period. Therefore, I need to aggregate the data by quarter, summing the number of transactions in each quarter for each unit.

```{r}
no_prior_floods_control <- no_prior_floods_control |>
    group_by(
        census_tract,
        t,
        G,
        geometry,
        pct_black_brown,
        pct_indigenous,
        mean_household_income,
        ditance_to_cbd,
        distance_to_nearest_water_body,
        distance_to_nearest_park
    ) |>
    summarise(
        transactions = sum(transactions),
    ) |>
    ungroup()
```

## Dropping the first quarters for the pre-treatment trends

Lastly, I will drop the first three quarters of the sample, so that there are some quarters before the first treatment period to allow the inspection of the pre-treatment trends. (It is worth noticing that, as we kept only the units that have not been treated in any period as control group, dropping the first quarters will make the treated group to be composed only by units that have been treated after the first three quarters, which is a desirable feature of the sample)

```{r}
no_prior_floods_control <- no_prior_floods_control |>
    filter(G > 3 | G == 0)
```

## Checking for unbalanced groups

```{r}
missing_tracts <- no_prior_floods_control |>
    sf::st_drop_geometry() |>
    group_by(census_tract) |>
    summarise(T = n_distinct(t)) |>
    filter(T < 12) |>
    arrange(desc(T))

missing_tracts |>
    DT::datatable()
```

## Running the CS2021 DID with multiple periods

```{r}
attgt <- did::att_gt(
    yname = "transactions",
    tname = "t",
    idname = "census_tract",
    gname = "G",
    xformla = ~ 1,
    clustervars = "census_tract",
    data = no_prior_floods_control
)

summary(attgt)
```

```{r}
ggdid(attgt)
```

```{r}
agg.simple <- aggte(attgt, type = "simple")
summary(agg.simple)
```

```{r}
agg.gs <- aggte(attgt, type = "group")
summary(agg.gs)
```

```{r}
ggdid(agg.gs)
```

```{r}
agg.es <- did::aggte(attgt, type = "dynamic")

summary(agg.es)
```

```{r}
ggdid(agg.es)
```

With the results above, no significant effect of flooding events on the number of transactions in the census tracts was found. So, the results don't support the hypothesis that flooding events have a significant impact on real estate liquidity in the census tracts. However, it is worth noticing that the number of transactions is a very rough measure of real estate liquidity, and further research could be done to investigate the impact of flooding events on real estate prices and time on the market, which are more direct measures of real estate liquidity.

# Running the CS2021 DID with multiple periods and covariates

## Selecting the covariates

Now, I will select some covariates to include in the model, to help on the evaluation of the possibility of violation of the parallel trends assumption on the first model. Revising some of the recent literature on the impact of flooding events on real estate prices, the variables tend to be a) related to the property itself, b) related to environmental amenities, and c) related to socioeconomic characteristics of the neighborhood. For the record, I'll enumerate the covariates used in four recent papers on the topic.

@chakraborty_social_2014 uses:

* Non-Hispanic black (%)
* Hispanic (%)
* Median household income ($)
* Below poverty (%)
* Median housing value ($)
* Vacant: seasonal/recreational use (%)

@zhang_flood_2016 uses:

* **Lnp:** Log of sales price
* **Living area:** Living area in 1000 ft²
* **Bedrooms:** # of bedrooms
* **Garage stalls:** # of garage stalls
* **Age:** Age of the house in years
* **One story:** = 1, if house style is one story
* **Two story:** = 1, if house style is two stories
* **Bilevel:** = 1, if house style is bi-level
* **Baths:** # of bathrooms
* **Attached garage:** = 1, if house has attached garage
* **Detached garage:** = 1, if house has detached garage
* **Ac:** = 1, if house has air conditioning
* **Water electronic:** = 1, if house has electronic water heater
* **Water gas:** = 1, if house has gas water heater
* **Water oil:** = 1, if house has oil water heater
* **Fireplace:** = 1, if house has fireplace
* **Wood deck:** = 1, if house has wood deck
* **Patio:** = 1, if house has patio
* **Poured foundation:** = 1, if house has poured foundation
* **Wood foundation:** = 1, if house has wood foundation
* **Slab foundation:** = 1, if house has slab foundation
* **Finished garage:** = 1, if garage is finished
* **Heated garage:** = 1, if garage is heated
* **Golf:** = 1, if house is abutting golf course
* **Park:** = 1, if house is abutting park
* **River:** = 1, if house is abutting river
* **Cass:** = 1, if house is located in Cass county

@zhang_flood_2019 uses: 

* **y:** Sales price
* **Livarea:** Living area in 1000 sqft
* **Bedrooms:** # of bedrooms
* **Garagestal:** # of garage stalls
* **Age:** Age of the house in years
* **Onestory:** =1, if house style is one story
* **Twostory:** =1, if house style is two stories
* **Bilevel:** =1, if house style is bi-level
* **Baths:** # of bathrooms
* **Atgarg:** =1, if house has attached garage
* **Ac:** =1, if house has air conditioning
* **Waterelect:** =1, if house has electronic water heater
* **Watergas:** =1, if house has gas water heater
* **Fireplace:** =1, if house has fireplace
* **Wooddeck:** =1, if house has wood deck
* **Patio:** =1, if house has patio
* **Pouredfd:** =1, if house has poured foundation
* **Woodfd:** =1, if house has wood foundation
* **Slab:** =1, if house has slab foundation
* **Finishedga:** =1, if garage is finished
* **Heatedga:** =1, if garage is heated
* **Golf:** =1, if house is abutting golf course
* **Park:** =1, if house is abutting park
* **River:** =1, if house is abutting river
* **Cass:** =1, if house is located in Cass county
* **Airport_Dist:** Distance to airport in miles
* **Citycenter_Dist:** Distance to city center in miles

@rajapaksa_impact_2017 uses:

* **R_PR:** House sale price adjusted to 2013 quarte 1 price
* **BEDRM:** Number of bed rooms
* **BATHRM:** Number of bathrooms
* **GARAGE:** Number of garage spaces
* **AREA:** Total area of land
* **Stories:** Number of stories in the house
* **Pool:** Dummy variable: 1 if a swimming pool is present, 0 otherwise
* **Garden:** Dummy variable: 1 if a garden is included and 0 otherwise. (The presence of well-maintained garden at the time of selling is considered as a presence of a garden)
* **ELEV:** Elevation
* **streem:** Distance in meters to the Brisbane river or stream (major creaks linked to the Brisbane river)
* **INCOME:** Medium household income in the mesh block (based on 2011 census and statistics survey)
* **parkdis:** Direct distance in meters to the closest park
* **highway:** Direct distance in meters to the highway
* **Time:** Months starting from 2006 January
* **afHT:** Time variable for high-income suburbs (time*high-income suburbs)
* **afMT:** Time variable for medium-income suburbs (time*medium-income suburbs)
* **afLT:** Time variable for low-income suburbs (time*low-income suburbs)
* **afHRD:** Distance in meters to the stream of high-income suburbs (streem*high-income suburb)
* **afMRD:** Distance in meters to the stream of medium-income suburbs (streem*medium-income suburb)
* **afLRD:** Distance in meters to the stream of low-income suburbs (streem*low-income suburbs)
* **afHEL:** Elevation of high-income suburbs (ELEV*high-income suburbs)
* **afMEL:** Elevation of medium-income suburbs (ELEV*medium-income suburbs)
* **afLEL:** Elevation of low-income suburbs (ELEV*low-income suburbs)

I don't have more details of the properties in the ITBI data, so I will use only the variables related to environmental amenities and socioeconomic characteristics of the neighborhood. Besides, as the ITBI data is aggregated at the census tract level, it doesn't seem appropriate to use variables related to the property itself.

So, by examining the variables used in the papers above, I will use the following covariates in the model:

* Black and brown population (%)
* Indigenous population (%)
* Mean household income ($)
* Direct distance to city CBD in meters
* Direct distance to the nearest body of water in meters
* Direct distance in meters to the closest park

The variables selected above are also adapted to the São Paulo context, as the variables related to the rivers are adapted to the Pinheiros and Tietê rivers, which are the main rivers in São Paulo, and the demographic variables are adapted to the Brazilian context.

Some of the variables above are available in the census data, while others are calculated from geospatial provided by the São Paulo City Hall digital map, named GeoSampa.

## Running the CS2021 DID with multiple periods and covariates

First I need to remove the census tracts that have missing values for any of the covariates and also check for support on each covariate,

```{r}
# Getting each census tract's covariates from data
missin_cov <- no_prior_floods_control |>
    sf::st_drop_geometry() |>
    group_by(census_tract) |>
    summarise(
        pct_black_brown = first(pct_black_brown),
        pct_indigenous = first(pct_indigenous),
        mean_household_income = first(mean_household_income),
        distance_to_cbd = first(ditance_to_cbd),
        distance_to_nearest_water_body = first(distance_to_nearest_water_body),
        distance_to_nearest_park = first(distance_to_nearest_park)
    ) |>
    filter(
        is.na(pct_black_brown) |
            is.na(pct_indigenous) |
            is.na(mean_household_income) |
            is.na(distance_to_cbd) |
            is.na(distance_to_nearest_water_body) |
            is.na(distance_to_nearest_park)
    ) |>
    pull(census_tract)

glimpse(missin_cov)
```

```{r}
library(modelsummary)

df_tab <- no_prior_floods_control |>
    filter(!census_tract %in% missin_cov) |>
    sf::st_drop_geometry() |>
    group_by(census_tract) |>
    summarise(
        pct_black_brown = first(pct_black_brown),
        pct_indigenous = first(pct_indigenous),
        mean_household_income = first(mean_household_income),
        distance_to_cbd = first(ditance_to_cbd) |> units::set_units("m") |> units::drop_units(),
        distance_to_nearest_water_body = first(distance_to_nearest_water_body) |> units::set_units("m") |> units::drop_units(),
        distance_to_nearest_park = first(distance_to_nearest_park) |> units::set_units("m") |> units::drop_units(),
        G = first(G),
        D = G > 0
    ) |>
    select(-G)

modelsummary::datasummary_balance(
    ~D,
    data=df_tab,
    dinm_statistic = "p.value"
)
```

```{r}
attgt <- did::att_gt(
    yname = "transactions",
    tname = "t",
    idname = "census_tract",
    gname = "G",
    xformla = ~ pct_black_brown + pct_indigenous + mean_household_income + ditance_to_cbd + distance_to_nearest_water_body + distance_to_nearest_park,
    clustervars = "census_tract",
    data = no_prior_floods_control |> filter(!census_tract %in% missin_cov)
)

summary(attgt)
```

```{r}
ggdid(attgt)
```

```{r}
agg.simple <- aggte(attgt, type = "simple", na.rm = TRUE)
summary(agg.simple)
```

```{r}
agg.gs <- aggte(attgt, type = "group", na.rm = TRUE)
summary(agg.gs)
```

```{r}
ggdid(agg.gs)
```

```{r}
agg.es <- did::aggte(attgt, type = "dynamic", na.rm = TRUE)

summary(agg.es)
```

```{r}
ggdid(agg.es)
```

# Running the Butts (2021) rings DID with multiple periods

As pointed out by @butts2021spill, there can be a bias in the CS2021 DID when there are spillover effects, which is a plausible scenario in the case of flooding events. Therefore, I will run the @butts2021spill rings DID with multiple periods, which is robust to spillover effects. The rings DID requires the definition of a treatment radius, which is the distance from the treated unit within which the control units are considered to be affected by the treatment. In this case, I will use a treatment radius of 1 km, but I will also run the model with other treatment radii to check the robustness of the results.

First, I will create the series of `Ring_ijt` variables, which indicate whether the unit is within the treatment radius of a treated unit in a given period. The `Ring_ijt` variables will be created for each treatment radius, and will be set to 1 if the unit is within the treatment radius of a treated unit in a given period, and 0 otherwise.

```{r}
df_spill <- no_prior_floods_control |>
  mutate(
    # Create D_it
    treat = as.numeric((G <= t) & (G != 0))
 )
```

```{r}
s = Sys.time()
s
```

```{r}
df_spill <- df_spill |>
  group_by(t) |>
  mutate(
    nearest_treated_dist = {
      treated_geom <- geometry[treat == 1]

      if (length(treated_geom) == 0L) {
        units::set_units(rep(NA_real_, n()), "m")
      } else {
        dmat_m <- st_distance(geometry, treated_geom) |>
          units::set_units("m") |>
          units::drop_units()

        units::set_units(apply(dmat_m, 1, min), "m")
      }
    },
    nearest_treated_dist_m = units::drop_units(nearest_treated_dist)
  ) |>
  ungroup()
```

```{r}
df_spill <- df_spill |>
  mutate(
    within_50 = !is.na(nearest_treated_dist_m) & nearest_treated_dist_m > 0 & nearest_treated_dist_m <= 50,
    within_50 = as.numeric(within_50),
    within_100 = !is.na(nearest_treated_dist_m) & nearest_treated_dist_m > 50 & nearest_treated_dist_m <= 100,
    within_100 = as.numeric(within_100),
    within_200 = !is.na(nearest_treated_dist_m) & nearest_treated_dist_m > 100 & nearest_treated_dist_m <= 200,
    within_200 = as.numeric(within_200),
    within_400 = !is.na(nearest_treated_dist_m) & nearest_treated_dist_m > 200 & nearest_treated_dist_m <= 400,
    within_400 = as.numeric(within_400),
    within_1000 = !is.na(nearest_treated_dist_m) & nearest_treated_dist_m > 400 & nearest_treated_dist_m <= 1000,
    within_1000 = as.numeric(within_1000),
    spill = !is.na(nearest_treated_dist_m) & nearest_treated_dist_m > 0 & nearest_treated_dist_m <= 1000,
    spill = as.numeric(spill)
  )
```

```{r}
e = Sys.time()
e
```

```{r}
print("Time taken to calculate the nearest treated distance and create the Ring_ijt variables:")
e-s
```

```{r}
df_spill <- df_spill |>
    mutate(rel_t = ifelse(G == 0, -1, t - G)) |>
    group_by(census_tract) |>
    mutate(
        t_within_50 = ifelse(any(within_50 == 1), min(t[within_50 == 1]), 0),
        rel_t_within_50 = ifelse(t_within_50 > 0 & treat != 1, t - t_within_50, -1),
        t_within_100 = ifelse(any(within_100 == 1), min(t[within_100 == 1]), 0),
        rel_t_within_100 = ifelse(t_within_100 > 0 & treat != 1, t - t_within_100, -1),
        t_within_200 = ifelse(any(within_200 == 1), min(t[within_200 == 1]), 0),
        rel_t_within_200 = ifelse(t_within_200 > 0 & treat != 1, t - t_within_200, -1),
        t_within_400 = ifelse(any(within_400 == 1), min(t[within_400 == 1]), 0),
        rel_t_within_400 = ifelse(t_within_400 > 0 & treat != 1, t - t_within_400, -1),
        t_within_1000 = ifelse(any(within_1000 == 1), min(t[within_1000 == 1]), 0),
        rel_t_within_1000 = ifelse(t_within_1000 > 0 & treat != 1, t - t_within_1000, -1),
        t_spill = ifelse(any(spill == 1), min(t[spill == 1]), 0),
        rel_t_spill = ifelse(t_spill > 0 & treat != 1, t - t_spill, -1),
        treat_or_spill = treat + within_50 + within_100 + within_200 + within_400 + within_1000
    ) |>
    ungroup()
```

```{r}
es_multi_ring <- did2s(
    data = df_spill |>
           sf::st_drop_geometry() |>
           filter(!census_tract %in% missin_cov) |>
           mutate(
                ditance_to_cbd = units::drop_units(ditance_to_cbd),
                distance_to_nearest_water_body = units::drop_units(distance_to_nearest_water_body),
                distance_to_nearest_park = units::drop_units(distance_to_nearest_park)
           ),
    yname = "transactions",
    # first_stage = ~ i(t, pct_black_brown) + i(t, pct_indigenous) + i(t, mean_household_income) +  i(t, ditance_to_cbd) + i(t, distance_to_nearest_water_body) + i(t, distance_to_nearest_park) |  census_tract + t,
    first_stage = ~ 0 | census_tract + t,
    # second_stage = ~ i(rel_t) + i(rel_t_within_50) + i(rel_t_within_100),
    # second_stage = ~ i(rel_t, ref=-1) + i(rel_t_within_50, ref=-1) + i(rel_t_within_100, ref=-1) + i(rel_t_within_200, ref=-1) + i(rel_t_within_400, ref=-1),
    # second_stage = ~ i(rel_t, ref=-1) + i(rel_t_within_50, ref=-1) + i(rel_t_within_100, ref=-1) + i(rel_t_within_200, ref=-1) + i(rel_t_within_400, ref=-1) + i(rel_t_within_1000, ref=-1),
    second_stage = ~ i(rel_t, ref = -1) + i(rel_t_spill, ref=-1),
    treatment = "treat_or_spill",
    cluster_var = "census_tract"
)
```

```{r}
iplot(es_multi_ring)
```


```{r}
summary(es_multi_ring)
```